R Notebook

### 2016-10-13 manuscript/important_references.Rmd
formatting
one more quick one

#Various factoids
---------------------
On North American climate
There has been an increase in mean temperature in North America since the 1980's (pg. 90, fig 2.7) 
Redmond, Kelly T., and John T. Abatzoglou. "Current climate and recent trends." Climate Change in North America. Springer International Publishing, 2014. 53-94.

Predictions for the next 10-20 years are uncertain (Meehl et al 2014) but models currently suggest a continued trend in warming, with potential for short term decreases (natural variability around increasing trend)(fig 3 & 4, Kumar et al 2014)
Kumar, Devashish, Evan Kodra, and Auroop R. Ganguly. "Regional and seasonal intercomparison of CMIP3 and CMIP5 climate model ensembles for temperature and precipitation." Climate dynamics 43.9-10 (2014): 2491-2518.
Meehl, Gerald A., et al. "Decadal climate prediction: an update from the trenches." Bulletin of the American Meteorological Society 95.2 (2014): 243-267.

>>>>

#Various factoids

On North American climate
There has been an increase in mean temperature in North America since the 1980's (pg. 90, fig 2.7)   
Redmond, Kelly T., and John T. Abatzoglou. "Current climate and recent trends." Climate Change in North America. Springer International Publishing, 2014. 53-94.

Predictions for the next 10-20 years are uncertain (Meehl et al 2014) but models currently suggest a continued trend in warming, with potential for short term decreases (natural variability around increasing trend)(fig 3 & 4, Kumar et al 2014)  
Kumar, Devashish, Evan Kodra, and Auroop R. Ganguly. "Regional and seasonal intercomparison of CMIP3 and CMIP5 climate model ensembles for temperature and precipitation." Climate dynamics 43.9-10 (2014): 2491-2518.  
Meehl, Gerald A., et al. "Decadal climate prediction: an update from the trenches." Bulletin of the American Meteorological Society 95.2 (2014): 243-267.  
-------------------------------
Biodiversity is an important thing to consider 
Cardinale, Bradley J., et al. "Biodiversity loss and its impact on humanity." Nature 486.7401 (2012): 59-67.
